---
title: "Week 02: COVID Visualization Activity"
date: "September, 11 2023"
author: "Joe Griffiths"
---

Today, we'll be working with a data set related to COVID.
This data is based on data from the the [COVID Tracking Project](https://covidtracking.com/).
I cleaned up this data and also added total populations from the 2020 for each of the relevant categories.
Note, due to differences in the way race and ethnicity are encoded in the census as compared to the the COVID Tracking Project, the population counts for LatinX may be somewhat inaccurate.

```{r load_data}
library(tidyverse)
load("CRDT Data.RData")
ls()
```

I've include 4 different data sets.
They all have the same data but have it represented in different ways.
Try using the different data sets and see which ones are good for making which plots.


```{r first_plot}
ggplot(covid_data_count, aes(x = date, y = Cases)) + geom_point()
```



If you want to only look at a specific state, you can do it like this.
For now, see what you can do just using `ggplot`.

```{r}
covid_data_count |> 
  filter(state == "MA") |> 
  ggplot(aes(x = date, y = Cases, color = race)) + geom_line()
```

1. Write code for a plot and describe what you observe?
2. Are there any conclusions you can draw?
3. What were you not able to do due to not having the R knowledge?
4. What other data would be useful to better understand this data?

#1 Plotting state case totals

covid_data_long |> 
  ggplot(aes(x = state))+ geom_bar()
  
subset_Covid_data_long_total_cases<-select(covid_data_long, race,count_type,count,state)
ggplot(aes(x=state)) + geom_bar()

##->had this before but wasn't what I meant... delete?    
#covid_data_long |> 
#   ggplot(aes(x = state, y = count_type, color = count_type)) + geom_point()

#2 [conclusions]
#3 I am currently unable to consolidate the states into regions (Northeast, Midwest, Pacific Northwest, etc.) and use these variables to get a neater and easier to read figure.
#4 It would be useful to have hospitalization data and test data from a bunch of the states that appear to be missing those two count types; it appears that all states at least have counts of deaths and cases.It also would be useful to know the overlaps between the deaths, hospitalizations, and tests. I looked on the COVIDtracking site and couldn't find any answers about the overlaps (although there is a lot on the site, so I could've missed it).